Analysis for Non-Expressive performances (ONSET)

### 2020-04-15 material/analysis/expression/stim_a/ioi_onset.Rmd
add ioi-analysis for performing-articulation
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r extract, include = FALSE}
dt_ioi <- fread("./preprocessor/filtered/data_onset.csv", header = T, sep = ",", dec = ".") # read a filtered csv

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)

# assign RowNr
dt_ioi$RowNr <- rep(1:72, nrow(dt_ioi)/72)
```

```{r normIOIs, include = FALSE}
# calculate normIOIs
dt_ioi$IOI <- diff(c(0, dt_ioi$TimeStamp))

# convert bpm to ms
dt_ioi[Tempo == 120]$Tempo <- 250
dt_ioi[Tempo == 110]$Tempo <- 273
dt_ioi[Tempo == 100]$Tempo <- 300

# normalise IOIs
dt_ioi$normIOI <- dt_ioi$IOI/dt_ioi$Tempo

# remove the first note
dt_ioi <- dt_ioi[RowNr != 1]

# assign Interval
dt_ioi$Interval <- rep(1:71, nrow(dt_ioi)/71)

# remove irrelevant intervals
ls_irrelevant <- list(c(25:28), c(32:35), c(51:52), c(56:57), c(65:71))
dt_ioi$EighthNote <- "Yes"

for (phrase in 1:length(ls_irrelevant)){
  for (note in 1:length(ls_irrelevant[[phrase]])){
    dt_ioi[Interval == ls_irrelevant[[phrase]][note]]$EighthNote <- "No"
  }
}
```

@@

```{r ioi, echo = FALSE}
# For each individual
ioi <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr)]
print(ioi)
```

@@

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Non-Expression")
p_ioi
```

@@

```{r ioi_seq, fig.width = 14, fig.height = 12, echo = FALSE}
# For each individual
ioi_seq <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), Mean = mean(normIOI)), by = .(SubNr, TrialNr, Interval)]

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, group = TrialNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  facet_grid(SubNr ~ .) +
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi[EighthNote == "Yes"], aes(x = normIOI)) +
  geom_histogram(binwidth = .02, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Non-Expression")
p_ioi_dis
```

@@

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[EighthNote == "Yes", .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.5)
p_cv_box
```

>>>>

```{r extract, include = FALSE}
dt_ioi_original <- fread("../trimmed/data_ioi_1.csv", header = T, sep = ",", dec = ".") # read a filtered csv
# Include only articulation
dt_ioi <- dt_ioi_original[Condition == "performing" & Skill == "articulation"]

# SubNr as a factor
dt_ioi$SubNr <- as.factor(dt_ioi$SubNr)
dt_ioi$TrialNr <- as.factor(dt_ioi$TrialNr)
```

@@

```{r ioi, echo = FALSE}
# For each individual
ioi <- dt_ioi[, .(N = length(normIOI), Mean = mean(normIOI), SD = sd(normIOI)), by = .(SubNr)]
print(ioi)
```

@@

```{r ioi_bar,  echo = FALSE}
p_ioi <- ggplot(data = ioi, aes(x = SubNr, y = Mean)) +
  geom_bar(stat = "identity", position = position_dodge()) +
  geom_errorbar(aes(ymin = Mean - SD, ymax = Mean + SD),
                width = .2, position = position_dodge(.9)) +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  labs(y = "Normalised IOI", subtitle = "IOI: Performing-Articulation")
p_ioi
```

@@

```{r ioi_seq, fig.width = 14, fig.height = 20, echo = FALSE}
# For each individual
ioi_seq <- dt_ioi[, .(N = length(normIOI), Mean = mean(normIOI)), by = .(SubNr, TrialNr, Interval)]

p_ioi_seq <- ggplot(data = ioi_seq, aes(x = Interval, y = Mean, group = TrialNr, colour = TrialNr)) +
  geom_line() +
  geom_point() +
  geom_hline(yintercept = 1, linetype = "dashed") + # Tempo
  facet_grid(SubNr ~ .) +
  labs(x = "Interval", y = "Normalised IOI") + scale_x_continuous(breaks=seq(1,66,1))
p_ioi_seq
```

@@

```{r ioi_dis, fig.width = 14, fig.height = 8, echo = FALSE}
p_ioi_dis <- ggplot(dt_ioi, aes(x = normIOI)) +
  geom_histogram(binwidth = .02, alpha = .5, position = "identity") +
  facet_grid(TrialNr ~ SubNr) +
  labs(x = "Normalised IOI", y = "Count", subtitle = "IOI: Performing-Articulation")
p_ioi_dis
```

@@

# IOI Variability
```{r cv, echo = FALSE}
# for each participant
cv <- dt_ioi[, .(N = length(normIOI), CV = sd(normIOI)/mean(normIOI)) , by = .(SubNr, TrialNr)]
cv
```

```{r cv_box, echo = FALSE}
p_cv_box <- ggplot(cv, aes(x = SubNr, y = CV)) +
  geom_boxplot() +
  geom_dotplot(binaxis = 'y', stackdir = 'center', dotsize = 0.3)
p_cv_box
```
